\begin{savequote}[8cm]
Alles Gescheite ist schon gedacht worden.\\
Man muss nur versuchen, es noch einmal zu denken.

All intelligent thoughts have already been thought;\\
what is necessary is only to try to think them again.
  \qauthor{--- Johann Wolfgang von Goethe }
\end{savequote}

\chapter{\label{ch:2-litreview}Model Building}

\minitoc

\section{Generating lepton masses and mixings with a heavy vector doublet}  

SM ``flavor puzzle'' motivates to build models with additional scalars
and fermions in their particle spectrum and with an extended gauge group,
supplemented by discrete flavour symmetries, which are usually spontaneously
broken, in order to generate the observed pattern of SM fermion masses and
mixing angles.

%%%%%%%%%%%% CITE ARTICLES HERE %%%%%%%%%%%%%%%%%%%%

 given the current lack of experimental evidence in favor
of the traditional big paradigms of Physics beyond the Standard Model, it
seems prudent to explore more exotic paths. In recent years, for instance,
some groups have pay attention to spin-1 fields transforming in the
fundamental representation of $SU(2)_L$ %\cite{Chizhov:2009fc}.
.This kind of
field may naturally appear, for instance, in models such as: Higgs-Gauge
Unification  % \cite{Maru:2018ocf} 
and Composite Higgs. 
%\cite{Agashe:2009bb,Franzosi:2016aoo}. 
In a previous paper, our group has studied the phenomenology of a spin-1 doublet which has the
same hypercharge of the Higgs doublet. %\cite{Saez:2018off}. 
In the context of Composite Higgs, this kind of field may be interpreted as a spin-1 excitation of the Higgs field in analogy
to the rho-mesons which can be seen as the spin-1 excitation of the pions. Such a spin-1 doublet cannot be coupled to standard fermions except by the introduction of exotic fields. The simplest alternative is the introduction ofa left-handed fermion which is singlet under the SM group. Of course, such an exotic fermion will behave like a sterile neutrino. In this case, the spin-1 doublet will couple the standard leptons to new exotic neutrino.We will show that the introduction of such new fields (the spin-1 doublet and the new sterile left-handed neutrino) can have an impact on
neutrino physics by providing a new mechanism for the mass generation of the
light active neutrinos. 




%\begin{mccorrection}

%\end{mccorrection}




\subsection{Discrete symmetries}

\subsection{Vector boson}

\subsection{CKM and PMNS matrices}

\subsection{Neutrino mass generation}   
